Analyzing Performance Bottleneck in Graph Neural Network Training: An Experimental View

### 2020-07-21 Manuscript/sec2-review-of-graph-neural-network.tex
修正sec2中gaan的错误

Different GNNs adopt different kinds of graph neurons and have different definitions of the three functions.
$\phi$ and $\Sigma$ are the \emph{edge calculation} functions.
They are conducted over every edge in $\mathcal{G}$.
$\gamma$ is the \emph{vertex calculation} function.
It is conducted over every vertex in $\mathcal{G}$.
\tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} list the edge functions and the vertex functions of typical GNNs, respectively.
For ChebNet, we report its GNN sub-layer in the tables. 
A ChebNet layer consists of $K$ GNN sub-layers and a summation layer:
$\boldsymbol{H}^{l+1} = \sum_{k=1}^K{\boldsymbol{Z}^{(k)} \textcolor{blue}{\boldsymbol{W}^{(k)}}}$ with the GNN sub-layers $\boldsymbol{Z}^{(1)}=\boldsymbol{H}^l$, $\boldsymbol{Z}^{(2)}=\hat{\boldsymbol{L}}\boldsymbol{H}^l$, and $\boldsymbol{Z}^{(k)}=2\hat{\boldsymbol{L}}\boldsymbol{Z}^{(k-1)} - \boldsymbol{Z}^{(k-2)}$, where $\boldsymbol{H}^l$ is the matrix of output hidden feature vectors of the layer $l-1$.
For GAT, a GAT layer consists of two sub-layers and it conducts part of the vertex calculation before the two sub-layers.
For GaAN, a GaAN layer consists of four sub-layers: the first sub-layer calculates the summation $\boldsymbol{m}_{j, i, (k)}^{l,0}  = \exp(\textcolor{blue}{FC_{\theta^{l, k}_{xa}}} (\boldsymbol{h}_j^l) \odot \textcolor{blue}{\boldsymbol{FC}_{\theta^{l,k}_{ya}}} (\boldsymbol{h}_i^l))$, and the other three layers calculate $\boldsymbol{m}^l_{j,i,1}$/$\boldsymbol{m}^l_{j,i,2}$/$\boldsymbol{m}^l_{j,i,3}$.

@@

						 & \boldsymbol{m}_{j, i, (k)}^{l,0}  = \exp(\textcolor{blue}{FC_{\theta^{l, k}_{xa}}} (\boldsymbol{h}_j^l) \odot \textcolor{blue}{\boldsymbol{FC}_{\theta^{l,k}_{ya}}} (\boldsymbol{h}_i^l)) \\

@@

						 & \alpha^l_{j, i, (k)} = \frac {\exp(\textcolor{blue}{FC_{\theta^{l, k}_{xa}}} (\boldsymbol{h}_j^l) \odot \textcolor{blue}{\boldsymbol{FC}_{\theta^{l,k}_{ya}}} (\boldsymbol{h}_i^l))} {\hat{\boldsymbol{a}}^{l, 0}_{i, (k)}}\\

@@

		to be the $LeakyReLU$ for activation functions and $FC_{\theta}(x)$ means applying no activation function after the linear transform.

>>>>

Different GNNs adopt different kinds of graph neurons and have different definitions of the three functions.
$\phi$ and $\Sigma$ are the \emph{edge calculation} functions.
They are conducted over every edge in $\mathcal{G}$.
$\gamma$ is the \emph{vertex calculation} function.
It is conducted over every vertex in $\mathcal{G}$.
\tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} list the edge functions and the vertex functions of typical GNNs, respectively.
For ChebNet, we report its GNN sub-layer in the tables. 
A ChebNet layer consists of $K$ GNN sub-layers and a summation layer:
$\boldsymbol{H}^{l+1} = \sum_{k=1}^K{\boldsymbol{Z}^{(k)} \textcolor{blue}{\boldsymbol{W}^{(k)}}}$ with the GNN sub-layers $\boldsymbol{Z}^{(1)}=\boldsymbol{H}^l$, $\boldsymbol{Z}^{(2)}=\hat{\boldsymbol{L}}\boldsymbol{H}^l$, and $\boldsymbol{Z}^{(k)}=2\hat{\boldsymbol{L}}\boldsymbol{Z}^{(k-1)} - \boldsymbol{Z}^{(k-2)}$, where $\boldsymbol{H}^l$ is the matrix of output hidden feature vectors of the layer $l-1$.
For GAT, a GAT layer consists of two sub-layers and it conducts part of the vertex calculation before the two sub-layers.
For GaAN, a GaAN layer consists of four sub-layers: the first sub-layer calculates the summation $\boldsymbol{m}_{j, i, (k)}^{l,0}  = \exp(<\textcolor{blue}{FC_{\theta^{l, k}_{xa}}} (\boldsymbol{h}_j^l) , \textcolor{blue}{\boldsymbol{FC}_{\theta^{l,k}_{ya}}} (\boldsymbol{h}_i^l)>)$, and the other three layers calculate $\boldsymbol{m}^l_{j,i,1}$/$\boldsymbol{m}^l_{j,i,2}$/$\boldsymbol{m}^l_{j,i,3}$.

@@

						 & \boldsymbol{m}_{j, i, (k)}^{l,0}  = \exp(<\textcolor{blue}{FC_{\theta^{l, k}_{xa}}} (\boldsymbol{h}_j^l), \textcolor{blue}{\boldsymbol{FC}_{\theta^{l,k}_{ya}}} (\boldsymbol{h}_i^l)>) \\

@@

						 & \alpha^l_{j, i, (k)} = \frac {\exp(<\textcolor{blue}{FC_{\theta^{l, k}_{xa}}} (\boldsymbol{h}_j^l), \textcolor{blue}{\boldsymbol{FC}_{\theta^{l,k}_{ya}}} (\boldsymbol{h}_i^l)>)} {\hat{\boldsymbol{a}}^{l, 0}_{i, (k)}}\\

@@

		to be the $LeakyReLU$ for activation functions and $FC_{\theta}(x)$ means applying no activation function after the linear transform.$<\cdot,\cdot>$ means the dot
		product between two vectors.
